CRUSE to Safe Cycling in Ireland \\\large{An Open Source Methodology to Support Active Travel}

### 2023-09-25 paper.qmd
Update with new results figure

# Uncomment for draft versions:
format: 
  html: default
  # docx: default
  # pdf: default

@@

@@

```{r}
# Results for one city

```

>>>>

# Uncomment for draft versions:
format: 
  html: default
#   # docx: default
#   # pdf: default

@@

```{r}
#| include: false
library(tidyverse)
library(tmap)
```

@@

```{r}
#| eval: false
#| echo: false
# Results for one city are shown below
city_name = "Dublin"
city_buffer = zonebuilder::zb_zone(city_name)
city_buffer_5km = city_buffer |>
  filter(circle_id <= 2)
# qtm(city_buffer_5km)
city_buffer_union = sf::st_union(city_buffer_5km)
rnet_fastest = sf::read_sf("./../testout/dublin/rnet_combined_fastest.gpkg")
rnet_fastest_city = sf::st_intersection(rnet_fastest, city_buffer_union)#
# nrow(rnet_fastest_city)
# table(rnet_fastest_city$`Bicycle (Go Dutch)`)
rnet_fastest_city_top = rnet_fastest_city |>
  filter(`Bicycle (Go Dutch)` != "1-10") |>
  filter(`Bicycle (Go Dutch)` != "0") |>
  mutate(across(`Bicycle (Baseline)`:`Quietness`, as.numeric)) |>
  slice_max(`Bicycle (Go Dutch)`, n = 10000)
m = tm_shape(rnet_fastest_city_top) +
  tm_lines(col = "Quietness", palette = "RdYlGn", lwd = 5)
tmap_save(m, "./images/rnet_fastest_city_top.png", width = 10, height = 10)
```

::: {#fig-city-results}

![](images/rnet_fastest_city_top.png)

Top 10,000 routes in Dublin by 'cycle friendliness' (quietness) based on the 'fastest' route network.

:::

### 2023-09-25 paper.tex
Update with new results figure

@@

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, breakable, frame hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

For non-professional users, the tool provides a simple interface to
explore the cycling potential of the network. By providing a single
landing page that is suitable for both professional and non-professional
users, the tool aims to facilitate communication between these groups.

@@

\caption{\label{fig-user-stories}User stories for the CRUSE tool}

@@

@@

>>>>

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

@@

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, enhanced, sharp corners, interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

For non-professional users, the tool provides a simple interface to
explore the cycling potential of the network. By providing a single
landing page that is suitable for both professional and non-professional
users (such as an advocate or parent interested in safe routes to
school), the tool aims to facilitate communication between these groups.

@@

\caption{\label{fig-user-stories}Hypothetical user stories for the CRUSE
tool illustrating that it can be used in different ways by different
user groups.}

@@

The main result of the CRUSE project is a new and open access web
application and dataset on current and potential future cycling levels
in Ireland, with evidence provided at county and route segment levels.
Like the PCT on which CRUSE builds, a key feature of the results is that
they are systematic and available for all counties, and most routes on
which cycling is permitted, in Ireland.

\hypertarget{sec-national-results}{%
\subsection{National results}\label{sec-national-results}}

The CRUSE tool provides estimates of cycling potential at the national
level, as shown in \textbf{?@fig-national-results}.

@@

\hypertarget{local-results}{%
\subsection{Local results}\label{local-results}}

To illustrate the results in urban areas, we took the top 4 cities in
Ireland by population: Dublin, Cork, Limerick and Galway. The results
for these cities are presented in Figure~\ref{fig-city-results}.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Results for one city are shown below}
\NormalTok{city\_name }\OtherTok{=} \StringTok{"Dublin"}
\NormalTok{city\_buffer }\OtherTok{=}\NormalTok{ zonebuilder}\SpecialCharTok{::}\FunctionTok{zb\_zone}\NormalTok{(city\_name)}
\NormalTok{city\_buffer\_5km }\OtherTok{=}\NormalTok{ city\_buffer }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{filter}\NormalTok{(circle\_id }\SpecialCharTok{\textless{}=} \DecValTok{2}\NormalTok{)}
\CommentTok{\# qtm(city\_buffer\_5km)}
\NormalTok{city\_buffer\_union }\OtherTok{=}\NormalTok{ sf}\SpecialCharTok{::}\FunctionTok{st\_union}\NormalTok{(city\_buffer\_5km)}
\NormalTok{rnet\_fastest }\OtherTok{=}\NormalTok{ sf}\SpecialCharTok{::}\FunctionTok{read\_sf}\NormalTok{(}\StringTok{"./../testout/dublin/rnet\_combined\_fastest.gpkg"}\NormalTok{)}
\NormalTok{rnet\_fastest\_city }\OtherTok{=}\NormalTok{ sf}\SpecialCharTok{::}\FunctionTok{st\_intersection}\NormalTok{(rnet\_fastest, city\_buffer\_union)}\CommentTok{\#}
\CommentTok{\# nrow(rnet\_fastest\_city)}
\CommentTok{\# table(rnet\_fastest\_city$\textasciigrave{}Bicycle (Go Dutch)\textasciigrave{})}
\NormalTok{rnet\_fastest\_city\_top }\OtherTok{=}\NormalTok{ rnet\_fastest\_city }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{filter}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Bicycle (Go Dutch)}\StringTok{\textasciigrave{}} \SpecialCharTok{!=} \StringTok{"1{-}10"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{filter}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Bicycle (Go Dutch)}\StringTok{\textasciigrave{}} \SpecialCharTok{!=} \StringTok{"0"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{mutate}\NormalTok{(}\FunctionTok{across}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Bicycle (Baseline)}\StringTok{\textasciigrave{}}\SpecialCharTok{:}\StringTok{\textasciigrave{}}\AttributeTok{Quietness}\StringTok{\textasciigrave{}}\NormalTok{, as.numeric)) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{slice\_max}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Bicycle (Go Dutch)}\StringTok{\textasciigrave{}}\NormalTok{, }\AttributeTok{n =} \DecValTok{10000}\NormalTok{)}
\NormalTok{m }\OtherTok{=} \FunctionTok{tm\_shape}\NormalTok{(rnet\_fastest\_city\_top) }\SpecialCharTok{+}
  \FunctionTok{tm\_lines}\NormalTok{(}\AttributeTok{col =} \StringTok{"Quietness"}\NormalTok{, }\AttributeTok{palette =} \StringTok{"RdYlGn"}\NormalTok{, }\AttributeTok{lwd =} \DecValTok{5}\NormalTok{)}
\FunctionTok{tmap\_save}\NormalTok{(m, }\StringTok{"./images/rnet\_fastest\_city\_top.png"}\NormalTok{, }\AttributeTok{width =} \DecValTok{10}\NormalTok{, }\AttributeTok{height =} \DecValTok{10}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{images/rnet_fastest_city_top.png}

\caption{\label{fig-city-results}Top 10,000 routes in Dublin by `cycle
friendliness' (quietness) based on the `fastest' route network.}
